Clustering four designs

### 2021-11-09 paper-supplementary.Rmd
supplementary done

# Raw data plot

@@

# Missing data plot
(ref:missing-data) Investigating the temporal location of missing values for customers who have implicit missing values. There are $13,735$ customers in the data set, with 8,685 having no missing values and the remaining $5,050$ having at least one missing value. Each cross represents a missed observation in time, while the line connecting two dots represents continuous missingness over time. Missing values occur at random times and do not appear to follow a pattern, although there is a higher concentration of missing values in September and October 2012 for the majority of customers. This plot is inspired by @wang2020tsibble.

@@

# Prototype selection

@@

S4. Run t-SNE using the default arguments on the complete data (sets the perplexity to equal 30 and performs random initialisation). We then create a linked tour with t-SNE layout with liminal as shown in Figure 4.

S5. We inspect of the subspace generated by the set of low-dimensional projections in tour by looking for a simplex shape while the visualization moves from one basis to another. When we brush the corners of the simplex, we find they fall on the edge of the t-SNE point cloud.
Hall, Marron, and Neeman (2005) have shown that in the extreme case of high-dimension, low-sample size data, observations are on the vertices of a simplex.

This is because in high-dimensional data analysis the curse of dimensionality reasons that points tend to be far away from the center of the distribution and on the edge of high-dimensional space. Contrary to this, is that projected data tends to clump at the center.

@@

```{r mds, out.width="100%", fig.cap="Instance selection using tours and projecting the points in a lower dimensional tsne cloud., eval = FALSE"}
knitr::include_graphics("figs/liminal_view.png")
```

@@

```{r JS-few}

@@

rownames(dist_mat_format) <- dist_mat$unique_data
```

```{r hier-clust-few}
d = stats::as.dist(dist_mat_format)
par(cex=0.5)
hc = stats::hclust(d,method="complete")
plot(hc)
```

```{r mds-plot-interact-few}
mds <- d %>%
  cmdscale() %>%
  as_tibble()

@@

mds_plot_10 <- ggplot(all_data_cluster,
       aes(x = Dim.1,
           y = Dim.2,
       color = groups, label = rownames(mds))) +
  geom_point(size = 1) +
  theme_classic()+
  theme(legend.position = "bottom") +
  scale_color_brewer(palette = "Dark2") +
  coord_fixed(ratio = 1)+
  theme(text = element_text(size = 6))

@@

rownames(dist_mat_format) <- dist_mat$unique_data
```

```{r hier-clust}
d = stats::as.dist(dist_mat_format)
par(cex=0.3)
hc = stats::hclust(d,method="complete")
plot(hc)
```

```{r mds-plot-interact}
mds <- d %>%
  cmdscale() %>%
  as_tibble()

@@

mds_plot_10 <- ggplot(all_data_cluster,
       aes(x = Dim.1,
           y = Dim.2,
       color = groups,
       label = rownames(mds))) +
  geom_point(size = 0.5) +
  theme_classic()+
  theme(legend.position = "bottom") +
  scale_color_brewer(palette = "Dark2") +
  coord_fixed(ratio = 1)

@@

```{r heatmap-interact, fig.height=8}
heatmap_raw <- data_q %>% 
  #select(unique_data, sim_data_quantile, id_facet, id_x) %>% 
  mutate(category = paste0("facet= ", id_facet, ",x= ", id_x)) %>% 
  unnest(sim_data_quantile) %>% 
  group_by(unique_data, category) %>% 
  mutate(D = row_number()) %>% 
  arrange(D, category) %>% 
  left_join(dist_mat, by = c("unique_data")) %>% 
  select(c(2:9))

@@

# Clustering all 350 customers

>>>>

@@

(ref:missing-data) Investigating the temporal location of missing values for customers who have implicit missing values. There are $13,735$ customers in the data set, with 8,685 having no missing values and the remaining $5,050$ having at least one missing value. Each cross represents a missed observation in time, while the line connecting two dots represents continuous missingness over time. Missing values occur at random times and do not appear to follow a pattern, although there is a higher concentration of missing values in September and October 2012 for the majority of customers. This plot is inspired by @wang2020tsibble.

@@

_Prototype selection_

@@

S4. Run t-SNE using the default arguments on the complete data (sets the perplexity to equal 30 and performs random initialisation). We then create a linked tour with t-SNE layout with R package liminal.

S5. We inspect of the subspace generated by the set of low-dimensional projections in tour by looking for a simplex shape while the visualization moves from one basis to another. When we brush the corners of the simplex, we find they fall on the edge of the t-SNE point cloud.

<!-- Hall, Marron, and Neeman (2005) have shown that in the extreme case of high-dimension, low-sample size data, observations are on the vertices of a simplex. -->

<!-- This is because in high-dimensional data analysis the curse of dimensionality reasons that points tend to be far away from the center of the distribution and on the edge of high-dimensional space. Contrary to this, is that projected data tends to clump at the center. -->

@@

```{r mds, out.width="100%", fig.cap="One instance of brushing in tours (right) and projecting the points in a lower dimensional tsne cloud (left).", out.height="200px"}
knitr::include_graphics("figs/tour-tsne.png")
```

@@

@@

rownames(dist_mat_format) <- dist_mat$unique_data
# write_rds(dist_mat_format, "validation/interact-4D/distmat_40series.rds")
# write_rds(dist_mat, "validation/interact-4D/distmat_40series_withnames.rds")
```

```{r hier-clust-few, fig.cap= "A dendogram showing the branching of $40$ series with each of the $4$ designs repeated $10$ times."}
d = stats::as.dist(dist_mat_format)
par(cex=0.5)
hc = stats::hclust(d,method="complete")
plot(hc)
rect.hclust(hc, k = 4, border = "red")

```{r mds-plot-interact-few, fig.cap= "MDS summary plot of $40$ series with each of the $4$ designs repeated $10$ times. It can be observed that all the series belonging to same design lie closer in this plot and all the ones in different designs are placed further away."}
mds <- d %>%
  cmdscale() %>%
  as_tibble()

@@

mds_plot_10 <- ggplot(all_data_cluster,
       aes(x = Dim.1,
           y = Dim.2,
       color = groups)) +
  geom_text(label = rownames(mds),check_overlap = TRUE)+
  geom_point(size = 1) +
  theme_classic()+
  theme(legend.position = "bottom") +
  scale_color_brewer(palette = "Dark2") +
  coord_fixed(ratio = 1)+
  theme(text = element_text(size = 6))

@@

rownames(dist_mat_format) <- dist_mat$unique_data
# write_rds(dist_mat_format, "validation/interact-4D/distmat_400series.rds")
# write_rds(dist_mat, "validation/interact-4D/distmat_400series_withnames.rds")
```

```{r hier-clust, fig.cap = "A dendogram showing the branching of $400$ series with each of the $4$ designs repeated $100$ times."}
d = stats::as.dist(dist_mat_format)
par(cex=0.5)
hc = stats::hclust(d,method="complete")
plot(hc)
rect.hclust(hc, k = 4, border = "red")
```

```{r mds-plot-interact, fig.cap= "MDS summary plot of $400$ series with each of the $4$ designs repeated $100$ times. It can be observed that all the series belonging to same design lie closer in this plot and all the ones in different designs are placed further away."}
mds <- d %>%
  cmdscale() %>%
  as_tibble()

@@

mds_plot_10 <- ggplot(all_data_cluster,
       aes(x = Dim.1,
           y = Dim.2,
       color = groups)) +
  #geom_text(label = rownames(mds),check_overlap = TRUE)+
  geom_point(size = 0.5) +
  theme_classic()+
  theme(legend.position = "bottom") +
  scale_color_brewer(palette = "Dark2") +
  coord_fixed(ratio = 1)

@@

```{r heatmap-interact, fig.height=8, fig.cap="A heatmap showing the cluster summary of $400$ series. Deciles of the clusters are plotted along the y-axis with each group on the x-axis faceted by each combination of the interacting granularity. The four distinct behavior across clusters are evident in all the combinations, with the first block corresponding to $data_null$. The deciles of the second block changes across both facet and x-axis. For similar reasons, the second, third and forth blocks correspond $data_varall$, $data_varf$ and $data_varx$ respectively." }
heatmap_raw <- data_q %>% 
  #select(unique_data, sim_data_quantile, id_facet, id_x) %>% 
  mutate(category = paste0("facet= ", id_facet, ",x= ", id_x)) %>% 
  unnest(sim_data_quantile) %>% 
  group_by(unique_data, category) %>% 
  mutate(D = row_number()) %>% 
  arrange(D, category) %>% 
  left_join(dist_mat, by = c("unique_data")) %>% 
  select(c(2:9))

@@

_Clustering all 350 customers_

### 2021-11-09 supplementary/algorithm1/real-data/cluster4-iter100.Rmd
supplementary done

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
read_chunk("R/simdata01.R")
```

@@

```{r nobs50, echo = TRUE}
ntimes_val = 50 # nobs per combination 
```

>>>>

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(here)
read_chunk(here::here("validation/simdata01.R"))
```

@@

```{r nobs50, echo = TRUE}
ntimes_val = 300 # nobs per combination 
```
